An Investigation of Confusing Code Patterns in JavaScript

### 2022-10-04 3_Method.tex
Making some modifications to address the reviwers comments, in particular pertaining to the reasons for having multiple studies.

By answering these research questions, we can either generalize or refute the findings about atoms of confusion already discussed in the literature (goal of research questions (RQ1) and (RQ2)). 
In addition, answering the third question allows us to enrich existing catalogs about atoms of confusion and discuss how often they occur in practice. Answering these research questions also lays the foundations for the implementation of tools that can automatically transform code into cleaner versions.
%---though we postpone these results to future research work.
We conduct a mixed-methods study to answer these questions. 
It includes two independently designed and conducted experiments: a repeated measures/within subjects study (Section~\ref{sec:meth:replication}) and one using a Latin square, counterbalancing experimental design to control for subject experience (Section~\ref{sec:meth:survey}). By using two different experiments, designed by different researchers, with different designs, and conducted with different participants, we hope to rigorously verify the impact of atoms of confusion in code comprehension activities. These two experiments explore the impact of atom candidates on understanding JavaScript code (goal of research question RQ1). They investigate whether or not programs that contain atom candidates tend to produce more misunderstanding for programmers trying to predict their outcome.% We leverage two independently-developed and conducted experiments with different designs to more  
We also conduct a set of interviews with developers (Section~\ref{sec:method:interview}) to contrast the quantitative results of the experiments with their preferences and opinions (thus addressing RQ2). Finally, we perform a repository mining study (Section~\ref{sec:method:msr}) that investigates the prevalence of some of these atom candidates in large scale, professionally-developed JavaScript software.

>>>>

By answering these research questions, we can either generalize or refute the findings about atoms of confusion already discussed in the literature (goal of research questions (RQ1) and (RQ2)). 
In addition, answering the third question allows us to enrich existing catalogs about atoms of confusion and discuss how often they occur in practice. Answering these research questions also lays the foundations for the implementation of tools that can automatically transform code into cleaner versions.
%---though we postpone these results to future research work.
We conduct a mixed-methods study to answer these questions. 
It includes two independently designed and conducted experiments: a repeated measures/within subjects study (Section~\ref{sec:meth:replication}) and one using a Latin square, between subjects, counterbalancing experimental design to control for subject experience (Section~\ref{sec:meth:survey}). By using two different experiments, designed by different researchers, with different designs, and conducted with different participants, we hope to rigorously verify the impact of atoms of confusion in code comprehension activities. \revised{Conducting multiple studies, with different designs and samples, is a typical approach in other areas of science to obtain more solid evidence and also to contest evidence obtained by single study, for example, Weggemans et al.~\cite{Weggemans:2001:DCE}. We discuss this matter further in Section~\ref{sec:whytwo}}.

These two experiments explore the impact of atom candidates on understanding JavaScript code (goal of research question RQ1). They investigate whether or not programs that contain atom candidates tend to produce more misunderstanding for programmers trying to predict their outcome.% We leverage two independently-developed and conducted experiments with different designs to more  
We also conduct a set of interviews with developers (Section~\ref{sec:method:interview}) to contrast the quantitative results of the experiments with their preferences and opinions (thus addressing RQ2). Finally, we perform a repository mining study (Section~\ref{sec:method:msr}) that investigates the prevalence of some of these atom candidates in large scale, professionally-developed JavaScript software.

### 2022-10-04 discussion.tex
Making some modifications to address the reviwers comments, in particular pertaining to the reasons for having multiple studies.

@@

@@

>>>>

In this section we discuss the results of the studies in combination.

%----------------------------------------------------------------------
\subsection{\revised{Contrasting the results of the studies}}\label{sec:contrast}

@@

%----------------------------------------------------------------------
\subsection{\revised{Addressing the research questions}}

@@

%----------------------------------------------------------------------
\subsection{\revised{Why multiple studies?}}\label{sec:whytwo}

\revised{It is not reasonable to consider something a scientific fact in an area as inexact as Software Engineering based on a single experiment. We present two independently-designed and conducted studies, with diverse code snippets, samples, and experimental designs, to provide stronger evidence. We believe that atom candidates confirmed to be atoms of confusion by both experiments arguably provide more reliable evidence of the potential to cause confusion of these code patterns for a wide range of developers, in diverse scenarios. That is the case for the Comma Operator and Assignment as Value atoms. Considering our work and others', there is little doubt that these are code patterns that lead to confusion. Furthermore, we complement the two experiments with interviews with 15 developers. Generally, in more mature areas of science, conducting multiple independent studies, potentially with different experimental designs, e.g., controlled vs. free-living experiments in the medical sciences~\cite{Weggemans:2001:DCE}, and examining their results in combination is the most reliable way of establishing truth.}

\castor{For the pros and cons of each approach, do you prefer lists of items or regular text paragraphs?}
\revised{The experimental designs we have employed in the two experiments have different trade-offs. The main advantages of having a repeated measures (or within subjects) study are the following: 
\begin{itemize}
  \item[+] They are better able to detect an effect size, given that one exists, since it is possible to collect data about both treatments from each participant. 
  \item[+] There tends to be less variance between groups, since the same participant is subject to both treatments
  \item[+] Individual differences between participants are controlled for because each participant acts as their own control
\end{itemize}
}
\revised{
\noindent
Conversely, the main limitations of a repeated measures study are the following: 
\begin{itemize}
\item[--] Data is not independent. This precludes the use of some statistical techniques and tests. 
\item [--] There is a potential learning/practice effect, since going through multiple examples may make the participants able to predict results of subsequent cases. This can be mitigated by separating examples pertaining to the same atom candidate, but not eliminated. 
\item [--] Fatigue effect, since participants have to examine more code snippets. This was exacerbated in our case, due to the larger number of atom candidates.
\end{itemize}}
\revised{
The Latin square study is an example of a between subjects study. In a way, its main advantages are precisely the absence (or a reduction) of the disadvantages of the repeated measures study and its main disadvantages are related to the advantages of a repeated measures study: 
\begin{itemize}
\item[+] Data is independent. 
\item[+] There is no possibility of learning/practice effect because each participant is only exposed to one treatment. 
\item[+] Fatigue effect is reduced, since each participant is only exposed to code snippets related to one of the treatments. 
\end{itemize}}
\revised{
\noindent
The main disadvantages of a between subjects study are the following:
\begin{itemize}
  \item[-] Effect sizes tend to be lower. 
  \item[-] Potentially more variance between groups since each participant is only required to be exposed to one treatment. 
  \item[-] Does not account for variance within groups.
\end{itemize}
The use of a Latin square mitigates some of the disadvantages intrinsic to a between subjects design. For example, since less work is required from participants, it was possible to obtain more data for the latin square study than we could get for the repeated measures study. This increases its statistical power, making it possible to detect smaller effect sizes.}

\revised{
In addition, to capture aspects that none of these studies can capture, e.g., personal impressions, we also leverage the interview study. Section~\ref{sec:contrast} highlights that some atoms that are perceived as confusing did not cause participants of the experiments to commit mistakes, e.g., Arithmetic as Logic. This combination of three different studies, with different samples and designs provides a more in-depth perspective on the extent to which these code patterns confuse JavaScript developers than we could obtain by having a single study. 
}
